### 2022-02-14 documentos/generators.tex
anotaciones
Fix all errors, all errors on the WORLD!!!!

PCE generators may be characterized by its local action on every qubit 
in the system. This action can be encoded using a vector index $\vec\alpha$, 
as in \eqref{eq:pauli_strings}, hence each of the different $4^N$ 
vector indices may be uniquely related to each of the PCE generators
and thus denoted as $\mcG_{\vec\alpha}$.
% \cpnote{
The proof is simplified if one uses the Kraus representation developed in 
\sref{sec:kraus}, so we postpone the demonstration to appendix \ref{sec:2_qubits}.
For single qubits, the identity corresponds to $\mcG_0$, shown in 
\fref{fig:one:qubit:examples}(b), whereas $\mcG_3$ is shown in in 
\fref{fig:one:qubit:examples}(c).
% }
The 2-qubits PCE generator represented in subfigure (c)
of \Fref{fig:examplesPCE} acts on the first qubit (first column) as mapping its
Bloch sphere to de $x$-axis, and on the second qubit (first row) acts an identity,
hence it is labeled $\mcG_{(1,0)}$.
See \Fref{fig:appex:twoQ_PCEGs} for the notation of all 2-qubit PCE generators.

A reflection symmetry is identified for both PCE generators $\pceg$ and
the matrix $A$ that diagonalizes the Choi matrix $\mcD_N$ of a PCE map.
The symmetry for a PCE generator $\pceg$ is encoded in the 
$N$-dimensional array of all $\taus$, the Cartesian grid associated with it 
is either symmetric or anti-symmetric under reflection of the 
indices in the $k$-th position in $\vec\alpha$ as
\begin{align}
\alpha_{0}\mapsto\alpha_3,\quad\alpha_{3}\mapsto\alpha_0,
\quad\alpha_1\mapsto\alpha_2, \quad\alpha_2\mapsto\alpha_1.
\end{align}
\janote{Aquí iría la prueva de la simetría de reflexión que está en el horno aún.}
For instance, see that the 2-qubit PCE generators 
$\mcG_{(1,0)}$, $\mcG_{(3,2)}$ and $\mcG_{(2,2)}$
represented in subfigures (c), (d) and (e) of \Fref{fig:two:qubit:examples}, 
respectively, are either symmetric or anti-symmetric under reflection with 
respect to lines that divide the diagram in half vertically and horizontally. 
The same symmetry is identified for the rows and columns of $A$ if one 
labels each position in a row or column $A^{(i)}$ as $A^{(i)}_{\vec\alpha}$.
\janote{Aquí habría que agregar la prueva de simetría para la $A$.}

>>>>

PCE generators may be characterized by its local action on every qubit 
in the system. This action can be encoded using a vector index $\vec\alpha$, 
as in \eqref{eq:pauli_strings}, hence each of the different $4^N$ 
vector indices may be uniquely related to each of the PCE generators
and thus denoted as $\mcG_{\vec\alpha}$.
% \cpnote{
The proof is simplified if one uses the Kraus representation developed in 
\sref{sec:kraus}, so we postpone the demonstration to appendix \ref{sec:2_qubits}.
\janote{referir a fig 5} For single qubits, the identity corresponds to $\mcG_0$, shown in 
\fref{fig:one:qubit:examples}(b), whereas $\mcG_3$ is shown in in 
\fref{fig:one:qubit:examples}(c).
% }
The 2-qubits PCE generator represented in subfigure (c)
of \Fref{fig:examplesPCE} acts on the first qubit (first column) as mapping its
Bloch sphere to de $x$-axis, and on the second qubit (first row) acts an identity,
hence it is labeled $\mcG_{(1,0)}$.
See \Fref{fig:appex:twoQ_PCEGs} for the notation of all 2-qubit PCE generators.

A reflection symmetry is identified for both PCE generators $\pceg$ and
the matrix $A$ that diagonalizes the Choi matrix $\mcD_N$ of a PCE map.
The symmetry for a PCE generator $\pceg$ is encoded in the 
$N$-dimensional array of all $\taus$, the Cartesian grid associated with it 
is either symmetric or anti-symmetric under reflection of the 
indices in the $k$-th position in $\vec\alpha$ as
\begin{align}
\Sigma: 0\mapsto3,\quad3\mapsto0,\quad1\mapsto2,\quad2\mapsto1
\end{align}
Indeed, any generator is a subspace containing half the elements of the full vector space.  
The map $\Sigma$ has the following properties
\begin{enumerate}
\item $\Sigma(\vec\alpha)+\Sigma(\vec\beta)=\vec\alpha+\vec\beta$.
\item $\Sigma(\vec\alpha)\neq\vec\alpha$
\end{enumerate}
From the first property, we now obtain
\begin{equation}
\vec\alpha=\Sigma(\vec\alpha)+\Sigma(\vec0)
\end{equation}
We now see that, depending on whether $\Sigma(\vec0)$ belongs (respectively does not belong) to the generator,
$\vec\alpha$ belongs to the generator if and only if $\Sigma(\vec\alpha)$ belongs (respectively does not belong) to the generator.

\janote{Aquí iría la prueva de la simetría de reflexión que está en el horno aún.}
For instance, see that the 2-qubit PCE generators 
$\mcG_{(1,0)}$, $\mcG_{(3,2)}$ and $\mcG_{(2,2)}$
represented in subfigures (c), (d) and (e) of \Fref{fig:two:qubit:examples}, 
respectively, are either symmetric or anti-symmetric under reflection with 
respect to lines that divide the diagram in half vertically and horizontally. 
The same symmetry is identified for the rows and columns of $A$ if one 
labels each position in a row or column $A^{(i)}$ as $A^{(i)}_{\vec\alpha}$.
\janote{Aquí habría que agregar la prueva de simetría para la $A$.}
